### 2021-06-22 Supplementary_Material/Supplementary_Material.Rmd
minor edits on supp mat.

 kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the full set of species (N = 1,506).") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

@@

kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the subset of sepcies with quantitative information of nectar and pollen.") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

>>>>

 kable(dat, longtable = T, booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S2.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis with the full set of species after outlier processing (N = 1,236).") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")

@@

kable(dat, longtable = T,"latex", booktabs = T,linesep = "\\addlinespace", escape=FALSE,  caption = "\\textbf{Table S3.} Loadings and explained variance of the first three principal components from the phylogenetically informed principal component analysis for the subset of species with quantitative information of nectar and pollen.") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "center")
